The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-07 paper/sections/results.tex
accidentally deleted fig label
fixed typos
update results and more typo fixes

  reported with appropriate units. $\rho$ is the applied density, \textbf{E} is the  Young's Modulus and $\mu$ is the Poisson's ratio.

@@

   \textbf{Example} & $|\vc{q}|$ & \textbf{Material}&  $\rho$(kg/m$^3$) & \textbf{E}(Pa) & $\mu$ &\textbf{Sample}(s) & \textbf{Quad}(s)& \textbf{Weights}(s) & \textbf{Build $\Pi$}(s) & \textbf{Step}(s) & \revise{\textbf{Nnz}(\%)} \\

@@

\reftbl{perf} shows the size of all our examples along with performance statistics and relevant parameters. 
\revise{We also plot the sparsity patterns of several stiffness matrices in our examples in \reffig{stiffness_sparsity}. }
Note that the individual parts of all models are \emph{not connected}, and no continuity constraints or constructive solid geometry operations have been applied. 
Rather, the SEM approach implicitly couples the boundary parts together to allow for seamless volumetric simulation. 
We use quadratic deformation for all the animation results, except the rocket (stiff) and starship which use linear deformation.
Models were created using Autodesk Fusion 360 \cite{AutodeskFusion360} and Rhinocerous 3D 7 \cite{mcneel-rhinoceros}. 
Please see the supplemental video for more animation results.

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/stiffness_sparsity.pdf}
  \caption{\revise{Our stiffness matrices can be sparse, while the corresponding matrix has to be dense in the traditional Boundary Element Method \cite{ArtDefo1999}. 
  Sparsity of our stiffness matrix is primarily determined by weight sparsity (number of non-zero weights at a given quadrature point) and polynomial order. }}
\end{figure}

@@

We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of 24 independent NURBS patches, shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, 
but very few surface elements are needed to produce compelling results.

@@

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/beam_twist.pdf}
  \caption{\revise{With the left end of the beam held fixed, we show the result of rotating the right end of the 22 part beam up to 360 degrees.}}
  \label{fig:twist}
\end{figure}

>>>>

  reported with appropriate units. $\rho$ is the applied density, \textbf{E} is the  Young's Modulus and \revise{$\nu$} is the Poisson's ratio.

@@

   \textbf{Example} & $|\vc{q}|$ & \textbf{Material}&  $\rho$(kg/m$^3$) & \textbf{E}(Pa) & \revise{$\nu$} &\textbf{Sample}(s) & \textbf{Quad}(s)& \textbf{Weights}(s) & \textbf{Build $\Pi$}(s) & \textbf{Step}(s) & \revise{\textbf{Nnz}(\%)} \\

@@

\reftbl{perf} shows the size of all our examples along with performance statistics and relevant parameters. 
\revise{We also plot the sparsity patterns of several stiffness matrices in our examples in \reffig{stiffness_sparsity}. }
Note that the individual parts of all models are \emph{not connected}, and no continuity constraints or constructive solid geometry operations have been applied. 
Rather, the SEM approach implicitly couples the boundary parts together to allow for seamless volumetric simulation. 
We use quadratic deformation for all the animation results, except the rocket (stiff) and starship which use linear deformation.
Models were created using Autodesk Fusion 360 \cite{AutodeskFusion360} and \revise{Rhinoceros} 3D 7 \cite{mcneel-rhinoceros}. 
Please see the supplemental video for more animation results.

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/stiffness_sparsity.pdf}
  \caption{\revise{Our stiffness matrices can be sparse, while the corresponding matrix has to be dense in the traditional Boundary Element Method \cite{ArtDefo1999}. 
  Sparsity of our stiffness matrix is primarily determined by weight sparsity (number of non-zero weights at a given quadrature point) and polynomial order. }}
  \label{fig:stiffness_sparsity}
\end{figure}

@@

We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of \revise{22} independent NURBS patches, shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, 
but very few surface elements are needed to produce compelling results.

@@

\revise{Additionally, we perform a twisting beam experiment on the 22 part beam model. Despite the relatively small number of NURBS patches, we see in \reffig{beam_twist} that the quadratic polynonmials permit complex deformation.}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/beam_twist.pdf}
  \caption{\revise{With the left end of the beam held fixed, we show the result of rotating the right end of the 22 part beam up to 360 degrees.}}
  \label{fig:beam_twist}
\end{figure}

\revise{We perform a basic scalability test shown in \reffig{scalability} by iteratively adding more degrees of freedom to a model and measuring average runtime of a simulation step, and report the ratio of number of nonzeros in the stiffness matrix. We begin with a unit cube composed of 6 parts and on each iteration we extend the cube, adding 4 more parts. The raycasting quadrature is updated on each
iteration so that a constant number of samples (45 in this case) lie in each cube. This experiment was performed using a AMD Ryzen 2600 with 16GB of RAM}

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.
\revise{In \reffig{octopus} we demonstrate the shape-aware nature of our algorithm on a  stable Neo-Hookean ~\cite{SNHkim} simulation of an octopus, and observe independent motion for each limb.}

@@
